A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Add BDDR function description

The complete code of $\text{BDD}_f$ and $\text{BDD}_R$ is listed
in~\cite[p. 432]{BURCH90}. However, both functions are described briefly in the
following paragraphs.

@@

>>>>

@@

The OBDD returned by $\text{BDD}_R \left( R, I_P \right)$ may contain both types
of variables, the place-holder and the individual variables, because a relational
term may contain free individual variables. Hence,
$\text{BDD}_R \left( R, I_P \right)$ is satisfied iff
$\mathcal{D} \left( R \right) \left( I_P \right) \left( I_D \right)$ holds for
the $n$-tuple $\langle I_A \left( d_1 \right), \ldots, I_A \left( d_n \right) \rangle$
for given $I_D$ and $I_A$, representing the interpretations for individual and
place-holder variables, respectively.

$\text{BDD}_R \left( R, I_P \right)$ distinguishes three cases:
\begin{enumerate}
    \item{If $R$ is a relational variable, $I_P \left( R \right)$ is returned.}
    \item{
        If $R$ is a $\lambda$-abstraction, an OBDD with substituted variables is
        returned, i.e. $\langle x_1 \leftarrow d_1, \ldots, x_n \leftarrow d_n \rangle$.
    }
    \item{
        If $R$ is fixed point computation, a helper function is called. This
        helper function computes the fixed point by a series of approximations
        $T_1, \ldots, T_k$, starting from an empty relation and terminating as
        soon as $T_{i+1} = T_i$, which can be tested easily using OBDD because
        equivalence testing can be done in constant time.
    }
\end{enumerate}

The complete code of $\text{BDD}_f$ and $\text{BDD}_R$ is listed
in~\cite[p. 432]{BURCH90}.
